Perturbed Gait Data

### 2014-11-26 paper.tex
Update paper.tex
Added acknowledgments.
update text to reflect new plot colors

The resulting output from the MATLAB script and Simulink produces a comma-
delimited text file of six columns: timestamp, slow, normal, and fast walking
perturbation signals, and slow and fast running signals.  These running signals
were generated in the event the testing protocol expanded from a walking study
to a running study, though they were not used in the data set.  The actual motion
of the treadmill belts are compared to the original input signals is shown in 
Figure~\ref{fig:input_output}.   The standard deviations of the outputs were 
calculated at 6.07\%, 9.68\%, and 12.68\% for the the 0.8, 1.2, and 
1.6 $m \cdot s^{-1}$ speeds, respectively.

\begin{figure}
  \includegraphics{figures/input_vs_output.pdf}
  \caption{Generated input signal (black) and actual treadmill belt movement
                (red) for average speeds of 0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:input_output}
\end{figure}

For further analysis, the input and output signals were transformed into the 
frequency domain through the Fast Fourier algorithm, and the results are
shown in Figure~\ref{fig:freq_analysis}.  It was observed that for the 1.2 $m \cdot s^{-1}$
average walking speed, the amplitude of the output is significantly lower 
than the amplitude of the input signal at lower frequencies.  Additionally, the 
amplitude of output signal in the 0.8 $m \cdot s^{-1}$ walking speed begins to attenuate 
around 2 Hz, which is a noticeably lower frequency than the other walking 
speeds.

\begin{figure}
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency analysis of the  input (black) and output (red)
                for average speeds of 0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}

@@

>>>>

The resulting output from the MATLAB script and Simulink produces a comma-
delimited text file of six columns: timestamp, slow, normal, and fast walking
perturbation signals, and slow and fast running signals.  These running signals
were generated in the event the testing protocol expanded from a walking study
to a running study, though they were not used in the data set.  The actual motion
of the treadmill belts are compared to the original input signals as shown in 
Figure~\ref{fig:input_output}.   The standard deviations of the outputs were 
calculated at 6.07\%, 9.68\%, and 12.68\% for the the 0.8, 1.2, and 
1.6 $m \cdot s^{-1}$ speeds, respectively.

\begin{figure}
  \includegraphics{figures/input_vs_output.pdf}
  \caption{Treadmill belt velocity input signals (purple) and recorded output 
                velocities (blue) for average belt speeds of 0.8, 1.2, and 1.6 m/s,
                respectively}
  \label{fig:input_output}
\end{figure}

For further analysis, the input and output signals for each average speed were
transformed into the frequency domain through the Fast Fourier algorithm, and 
the results are shown in Figure~\ref{fig:freq_analysis}.  It was observed that for
the 1.2 $m \cdot s^{-1}$ average walking speed, the amplitude of the output is 
significantly lower than the amplitude of the input signal at lower frequencies.  
Additionally, the amplitude of output signal in the 0.8 $m \cdot s^{-1}$ walking
speed begins to attenuate around 2 Hz, which is a noticeably lower frequency than
the other walking speeds.

\begin{figure}
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency analysis of the treadmill belt velocity input signal 
                 (purple) and the recorded output velocity (blue)
                for average belt speeds of 0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}

@@

\section{Acknowledgments}
We thank Roman Boychuk and Obinna Nwanna for assistance with the experiments.  The work was partially funded by the
State of Ohio Third Frontier Commission through the Wright Center for Sensor Systems Engineering (WCSSE).
